Aneuploidy can be an evolutionary diversion\\ on the path to adaptation

### 2024-01-11 ms/ms.tex
add anna and petra; revise title

% Title page
% Chromosomal duplication is a transient evolutionary solution to stress
% \title{Chromosomal duplication can be an evolutionary detour on the path to adaptation}
\title{Aneuploidy can be an evolutionary detour \\ on the path to adaptation}

@@

\author[a,b,1]{Ilia Kohanovski}
\author[a,1]{Martin Pontz}
\author[c]{Orna Dahan}
\author[c]{Yitzhak Pilpel}
\author[d]{Avihu H. Yona}
\author[a,*]{Yoav Ram}

\affil[a]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[b]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[c]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot, Israel}
\affil[d]{Institute of Biochemistry, Food Science and Nutrition,
Robert H. Smith Faculty of Agriculture, Food and Environment,
The Hebrew University of Jerusalem, Israel}
\affil[1]{These authors contributed equally to this work}
\affil[*]{Corresponding author: yoav@yoavram.com}

>>>>

% Title page
% Chromosomal duplication is a transient evolutionary solution to stress
% \title{Chromosomal duplication can be an evolutionary detour on the path to adaptation}
\title{Aneuploidy can be an evolutionary diversion\\ on the path to adaptation}

@@

\author[a,b,1]{Ilia Kohanovski}
\author[a,1]{Martin Pontz}
\author[c]{P\'{e}tra Vande Zande}
\author[c]{Anna Selmecki}
\author[d]{Orna Dahan}
\author[d]{Yitzhak Pilpel}
\author[e]{Avihu H. Yona}
\author[a,*]{Yoav Ram}

\affil[a]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[b]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[c]{Department of Microbiology and Immunology, University of Minnesota Medical School, Minneapolis, MN}
\affil[d]{Department of Molecular Genetics, Weizmann Institute of Science, Rehovot, Israel}
\affil[e]{Institute of Biochemistry, Food Science and Nutrition, Robert H. Smith Faculty of Agriculture, Food and Environment, The Hebrew University of Jerusalem, Israel}
\affil[1]{These authors contributed equally to this work}
\affil[*]{Corresponding author: yoav@yoavram.com}
